---
title: "Toronto Marriage Licence Statistics"
subtitle: "Discussions and Graphs"
author: 
  - Ruiyang Wang
thanks: "Code and data are available at: https://github.com/Ruiyang-Wang/STA304-Week3."
date: today
date-format: long
abstract: "This study analyzes the marriage licence statistics for Toronto, focusing on marrying trends over recent years."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
setwd("/home/rstudio/STA304 Week3/starter_folder-main-master")
data <- read_csv(("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @talia, @opendatatoronto, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of marriage (@fig-marriage), from @opendataatoronto.

```{r}
#| label: fig-marriage
#| fig-cap: Marriage date and licences
#| echo: false

 data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```






# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


aa`   
